Effects of the body force on the evacuation dynamics

### 2019-12-26 paper.tex
Update paper.tex

We measured the maximum forces attainable at the subway in Buenos Aires, 
Argentina. Our preliminary results show that pedestrians feel uncomfortable 
whenever a body force ranging from $5$ to $20\,$N is applied for at least ten 
minutes. Short lasting forces (say, less than 4 minutes) may also be perceived 
as uncomfortable for values ranging from $10$ to $30\,$N. We also recorded body 
forces up to $60\,$N during very short ``hits''. The comparison with the 
fittings provided by Ref.~\cite{song_2019} shows that these magnitudes 
accomplish densities around 5 people/m$^2$.     \\

>>>>

We measured the maximum attainable forces at the subway in Buenos Aires, 
Argentina. Our preliminary results show that pedestrians feel ``uncomfortable'' 
whenever a body force ranging from $5$ to $20\,$N is applied for at least ten 
minutes. Short lasting forces (say, less than 4 minutes) may also be perceived 
as ``uncomfortable'' for values ranging from $10$ to $30\,$N. We also recorded body 
forces up to $60\,$N during very short ``hits''. The comparison with the 
fittings provided by Ref.~\cite{song_2019} shows that these magnitudes 
accomplish densities around 5 people/m$^2$.     \\
